---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Treggae

<!-- badges: start -->
[![R-CMD-check](https://github.com/imbeimainz/Treggae/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/imbeimainz/Treggae/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`Treggae` is your dancing companion for exploring gene signatures in the context
of T-regs (T regulatory cells) - and not only

## Installation

You can install the development version of Treggae like so:

``` r
remotes::install_github("imbeimainz/Treggae")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library("Treggae")
Treggae::signature("signature_name")

Treggae::list_signatures()
```

## Code of Conduct

Please note that the Treggae project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
